Untitled

### 2024-02-05 MSR.rmd
Update

@@

@@

>>>>

![](images/clipboard-1137921527.png){width="336"}

@@

![](images/clipboard-2482589517.png){width="333"}

@@

## Poisson

![](images/clipboard-3888260971.png){width="390"}

![](images/clipboard-3043575602.png){width="391"}

```{r}
#Poisson(1) melalui ekponensial  
i <- 1000
lambda <- 1  
K <- NULL
for (z in 1:i){ 
  sk <- 0  
  k <- 0
  while (sk<=1){
    u <- runif(1)
    y <- -log(u)/lambda 
    sk <- y+sk
    k <- k+1 
  }
  K[z] <- k-1 
}
(tabel <- table(K)/length(K)) 
barplot(tabel)

#Poisson(1) melalui seragam  
i <- 1000
lambda <- 1  
K <- NULL
for (z in 1:i){ 
  k <- 0
  sk <- 1
  while(sk >= exp(-lambda)){  
    u <- runif(1)
    sk <- sk*u 
    k <- k+1
  } 
  K[z] <- k
}
(tabel <- table(K)/length(K)) 
barplot(tabel)
```
